Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-05 paper/ms.tex
update manuscript
cleaning repo

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines were found. To set limits on the contributions of a close-by
star to the observed spectrum, we injected a second set of lines to
the mean least-squares deconvolution profile derived from the CHIRON
observations. The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$. The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.

@@

Our model for time-series photometry data was an
\citet{exoplanet:agol19} transit with physical and orbital parameters
shared across all transit windows, plus a local quadratic trend
allowed within each window.  Select parameters and priors are listed
in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
fitted for the shared stellar parameters $\{\log g, R_\star, u_0,
u_1\}$, and the shared planetary parameters $\{t_0, P, b, \log(R_{\rm
p}/R_\star)\}$.  There were also three free trend parameters for each
transit window to account for the local rotational variability.  In
the TESS-only model this yielded 23 free parameters, of which 8 were
physically relevant and 15 were nuisance parameters.  In the combined
TESS and ground-based model, there were an additional 7 transits, and
therefore an additional 21 nuisance parameters for a total of 44 free
parameters.

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{ceres} \citep{brahm_2017_ceres},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano},
	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  \texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\

>>>>

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines was found. To set limits on the contributions of a close-by
star to the observed spectrum, we injected a second set of lines to
the mean least-squares deconvolution profile derived from the CHIRON
observations. The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$. The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.

@@

Our model for time-series photometry data was an
\citet{exoplanet:agol20} transit with physical and orbital parameters
shared across all transit windows, plus a local quadratic trend
allowed within each window.  Select parameters and priors are listed
in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
fitted for the shared stellar parameters $\{\log g, R_\star, u_0,
u_1\}$, and the shared planetary parameters $\{t_0, P, b, \log(R_{\rm
p}/R_\star)\}$.  There were also three free trend parameters for each
transit window to account for the local rotational variability.  In
the TESS-only model this yielded 23 free parameters, of which 8 were
physically relevant and 15 were nuisance parameters.  In the combined
TESS and ground-based model, there were an additional 7 transits, and
therefore an additional 21 nuisance parameters for a total of 44 free
parameters.

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{ceres} \citep{brahm_2017_ceres},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano},
	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  \texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\
